---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Load and preprocess the data
Read the data file and print the first few lines for inspection. 
```{r}
data <- read.csv("activity.csv")
head(data)
```

There are missing values, so index the vector accordingly. 
```{r}
bad <- is.nan(data$steps)
```

Combine the date and interval variables into an R time object. Since strptime() cannot handle the hhmm format we will need to

1. Add leading zeros to the interval variable, 
1. Split it up into two segments with substr(), 
1. Feed into strptime() as %h%m, and 
1. Print the top of the array for inspection. 

```{r}
# Four element time format array: 
time <- sprintf('%04i', data$interval)
datetime <- strptime(paste(data$date, substr(time,1,2), 
            substr(time,3,4)), '%Y-%m-%d %H %M', 
            tz="EST5EDT")
head(datetime)
```

How many days do our data cover? 
```{r}
> difftime(tail(datetime, n=1), datetime[1])
```

## What is mean total number of steps taken per day?

Sum steps per day and produce a vector containing those values. 



```{r}
datetime[1]; tail(datetime, n=1)
```

This means we can add up steps in bunches of 24 (hours in a day) times 12 (entries per hour, given the five-minute interval), that is, 288 time steps for each day. 

```{r}
ndays <- length(datetime)/(24*12)
ndays
```

**The integer daily average number of steps is:**

```{r}
round(sum(data$steps, na.rm=TRUE)/ndays)
```

Now let's make a histogram. 

## What is the average daily activity pattern?

Produce a plot of steps per hour


## Inputing missing values



## Are there differences in activity patterns between weekdays and weekends?
